Automatic Matching of Bullet Lands

### 2015-12-27 imaging-paper.Rnw
discussion of bullets

\hh{The main idea of locally weighted regression is to use a weighting routine that  emphasizes the effect of points close by and de-emphasizes the effect of points as they are further away. The weighting function used here, is the tricubic function $w(d) = (1 - d^3)^3$, for $d \in [0,1]$ and $w(d) = 0$ otherwise.  $d$ is defined as the the distance between $x_i$ and the location of the fit $x_o$ and the maximum distance of the range of the $x$-values for span $\alpha$ in $x_o$. }

\hh{XXX standard errors: are based on independence of errors (which we don't have because of the high autocorrelation) and the assumption that the amount of bias is neglible. Which we don't know. We can produce standard errors, but (a) the nominal confidence level will be violated, and (b) the errors only allow for pointwise errors. We need a different approach. XXX}

Figure~\ref{fig:loess_fit} provides a look at the loess fit, in blue, overlaid against the processed image of bullet~1-5. The fit seems to do a reasonable job of capturing the structure of the image. Figure~\ref{fig:loess_resid} shows the residuals from this fit. These residuals are called the \emph{signature} of bullet~1-5.
%
\begin{figure}[hbtp]
  \centering
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{\label{fig:loess_fit} Loess fit for bullet~1-5.}
<<loess_fit, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE,  message=FALSE>>=

@@

my.loess$fitted + ylab("Surface measurements")
@
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{\label{fig:loess_resid} Residuals of loess fit for bullet~1-5.
This defines the {\it signature} of bullet~1-5. Blue areas show  95\% bootstrap confidence intervals (based on $B=1,000$ bootstrap samples).
}
%<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
%my.loess$resid + ylab("Residuals of loess Fit") 
%@
<<boot_loess, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
boot.loess <- boot_fit_loess(br111_bullet, br111.groove)
poly <- with(boot.loess, data.frame(x = c(y,rev(y)), y=c(high, rev(low))))
qplot(x=x, y=y, geom="polygon", fill=I("steelblue"), data=poly) +
  geom_line(aes(x=y, y=resid), data=my.loess$data) +
  ylab("Residuals of loess fit") + xlab("y") + theme_bw()
@
\end{subfigure}
\caption{Fit and residuals of a loess fit to bullet~1-5 (Barrel~1).}
\end{figure}
%
Figure~\ref{fig:loessfits} shows the signatures of all lands of bullet 2 (in grey) fired from the same barrel as bullet~1. The darker line overlaid on each of the signatures, shows signature from bullet~1-5. 
%We can reproduce a similar figure to the one from the circular fits by overlaying the residuals from each loess fit for bullet 2 onto an image of the loess residuals from bullet~1-5. This is shown in Figure~\ref{fig:loessfits}. 
Bullet 2-1 is the best match for bullet~1-5, but the alignment is not quite  correct.

\begin{figure}[hbtp]
  \centering
<<loessfits, echo=FALSE, fig.width=10, fig.height=5, out.width='\\textwidth', warning=FALSE>>=
br121.groove <- get_grooves(br121_bullet)
br122.groove <- get_grooves(br122_bullet)
br123.groove <- get_grooves(br123_bullet)
br124.groove <- get_grooves(br124_bullet)
br125.groove <- get_grooves(br125_bullet)
br126.groove <- get_grooves(br126_bullet)

my.loess1 <- fit_loess(br121_bullet, br121.groove)
my.loess2 <- fit_loess(br122_bullet, br122.groove)
my.loess3 <- fit_loess(br123_bullet, br123.groove)
my.loess4 <- fit_loess(br124_bullet, br124.groove)
my.loess5 <- fit_loess(br125_bullet, br125.groove)
my.loess6 <- fit_loess(br126_bullet, br126.groove)

my.loessactual <- fit_loess(br111_bullet, br111.groove)

minrows <- min(length(my.loess1$data$resid),
               length(my.loess2$data$resid),
               length(my.loess3$data$resid),
               length(my.loess4$data$resid),
               length(my.loess5$data$resid),
               length(my.loess6$data$resid),
               length(my.loessactual$data$resid))

my.df <- data.frame(y = my.loess1$data$y[1:minrows], resid1 = my.loess1$data$resid[1:minrows],
                    resid2 = my.loess2$data$resid[1:minrows], resid3 = my.loess3$data$resid[1:minrows],
                    resid4 = my.loess4$data$resid[1:minrows], resid5 = my.loess5$data$resid[1:minrows],
                    resid6 = my.loess6$data$resid[1:minrows])

melt.df <- my.df %>%
    gather(key = part, value = resid, resid1:resid6)
melt.df$part <- gsub("resid", "", melt.df$part)

actual.df <- my.loessactual$data[1:minrows,]
melt.df$land <- melt.df$part
qplot(y, resid, data=melt.df, #colour=factor(x), 
      geom="line", size=I(.75), colour=I("grey70")) + 
  facet_wrap(~land, ncol=3, labeller="label_both") + 
  scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(data = actual.df, aes(y, resid), colour="black", size=.75, alpha=0.5) + ggtitle("Signatures of bullet 1 in grey, bullet 1-5 in black") + ylab("Residuals of loess fit")
@    
\caption{\label{fig:loessfits} Residuals of a loess fit to bullets 1 and 2 from barrel 1. Bullet~1-5 is shown in black. }
\end{figure}

@@

\begin{figure}[hbtp]
\centering
    \begin{subfigure}[t]{\textwidth}\centering
\caption{Loess smooth of signatures  at $x = 100$ (span is 0.03).\label{fig:smooth}}{%
<<smooth, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3.5, out.width='.65\\textwidth', warning=FALSE>>=
qplot(data=lofX, y, resid, colour=I("grey30"), size=I(0.75), geom="line", group=bullet) +
  geom_line(aes(y=l30), colour="grey70", size=0.5) +
  facet_grid(bullet~.) +
#  scale_colour_manual("", values=cols) +
  theme_bw() + ylab("") + 
  theme(legend.position="none")
@
    }
\end{subfigure}
\begin{subfigure}[t]{\textwidth}\centering
\caption{Using a rolling median peaks and valleys are identified for each signature. \label{fig:smoothcutb}}{%
<<smoothcut, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3.5, out.width='.65\\textwidth', warning=FALSE>>=
#images <- file.path(datadir, dir(datadir))
  lof <- processBullets(paths = images[c(5,7)], x = 100)
  lof <- bulletSmooth(lof)
  bAlign = bulletAlign(lof)
  lofX <- bAlign$bullet

@@

  ggplot() + theme_bw() +
    geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), ymin=-6, ymax=6, 
              data=peaks,  alpha=0.2) +
    geom_vline(aes(xintercept=extrema, colour=factor(type)), 
               data= peaks, alpha=0.7) +
    scale_colour_brewer(palette="Set2") + 
    scale_fill_brewer(palette="Set2") +
    theme(legend.position="none") + 
    facet_grid(bullet~.) +
    geom_line(aes(x=y, y=l30, group=bullet), data=lofX) +
  ylab(expression(paste("Signatures (in ",mu,"m)", sep=""))) 
@
}
\end{subfigure}    
\begin{subfigure}[t]{\textwidth}\centering
    \caption{Rectangles in the back identify a line on one of the bullets.  Matching striation marks are indicated by color filled rectangles and marked by an `o'. Mismatches are filled in grey and  marked by an `x'.   \label{fig:smoothcutd}}{%
<<smoothmatch, echo=FALSE, dependson='twolands100match', fig.width=7, fig.height=2.75, out.width='.65\\textwidth', warning=FALSE>>=
peaks1$lines$bullet <- b12[1]
peaks2$lines$bullet <- b12[2]

@@

All of the other steps are done on pairs of bullet lands:
\begin{enumerate}
\item {\bf Smooth the two signatures} by a loess with a very small span (see Figure~\ref{fig:smooth}). 
\item Use cross-correlation to {\bf find the best alignment} of the two signatures: shift one of the signatures by the lag indicated by the cross-correlation function (see Figure~\ref{fig:ccf} for the cross-correlation function and Figure~\ref{fig:crosscutX} for the resulting shift).
\item Using a rolling average, {\bf identify peaks and valleys} for each of the signatures. We then define an interval around the location of the extrema on each side as one third of the distance to the location of the next extrema (see Figure~\ref{fig:smoothcutb}). 
\item {\bf Match striations across signatures:} based on the intervals around the extrema as defined above, we identify joint intervals between two signatures as those areas, in which two or more of the individual intervals overlap: a joint interval is defined as the smallest interval that encompasses all of the overlapping intervals. A joint interval is then called a match(ing stria) between the signatures, if all of the intervals are of the same type of extrema, i.e.\ they are either all peaks or all valleys. In Figure~\ref{fig:match} all matches are shown as color-filled rectangles corresponding to their type of extrema (peaks are shown in orange, and valleys in green). Non-matching intervals are left grey.
\item {\bf Extract features from the aligned signatures and the matches between them:} there is a slew of different features one could extract. Here, we describe a few of the ones that can be found in the literature and some that we found to be of practical relevance:
\begin{enumerate}[label=(\roman*)]
\item maximal number of CMS (consecutive matching striae), and, similarly, the number of consecutively non-matching striae (CNMS), 
\item number of matches and non-matches,
\item average difference between signatures $D$, defined as the Euclidean vertical distance of surface measurements between aligned signatures. Let $f(t)$ and $g(t)$ be smoothed, aligned signatures:
\[
D^2 = \frac{1}{\text{\#}t}\sum_t (f(t) - g(t))^2,
\]
\item the sum $S$ of matched extrema: for each of the matched stria, determine the average of the absolute height of the peak or valley. $S$ is then defined as the sum of all these averages. 
\end{enumerate}
\end{enumerate}
%
The difference $D$ between signatures is here defined as the Euclidean distance (in $\mu m$). In the paper by \citet{ma:2004}, distance is defined as a measure relative to the first signature, which serves as a comparison reference and is therefore a unitless quantity.

@@

\begin{figure}[hbtp]
  \centering
<<barrel2, echo=FALSE, fig.width = 10, fig.height=6, out.width='\\textwidth', warning=FALSE>>=

list_of_matches <- lapply(25:30, function(i) {
  lof <- processBullets(paths = images[c(31,i)], x = 100)
  lof <- bulletSmooth(lof)

  bAlign = bulletAlign(lof)
  lofX <- bAlign$bullet

  b12 <- unique(lof$bullet)
  peaks1 <- get_peaks(subset(lofX, bullet==b12[1]), smoothfactor = 25)
  peaks2 <- get_peaks(subset(lofX, bullet == b12[2]), smoothfactor = 25)
  peaks1$lines$bullet = b12[1]
  peaks2$lines$bullet = b12[2]
  lines <- striation_identifyXXX(peaks1$lines, peaks2$lines)

  ggplot() +
    theme_bw() + 
    geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), show.legend=FALSE, ymin=-6, ymax=6, data=lines, alpha=0.2) +
    geom_line(aes(x = y, y = l30, linetype = bullet),  data = lofX, alpha=0.6) +
    scale_linetype_discrete("") +
    scale_fill_brewer("", palette="Set2", na.value=alpha("grey50", alpha=0.5)) +
  theme(legend.position = c(1,1.2), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4))) + 
    ylim(c(-6,6)) + ylab("") + xlab("") +
    geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(lines, !match)) +
    geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(lines, match)) +
    theme(plot.margin=unit(c(1,0,0,0), unit="line"))
})

grid.arrange(list_of_matches[[1]], list_of_matches[[2]], list_of_matches[[3]], 
             list_of_matches[[4]], list_of_matches[[5]], list_of_matches[[6]],
             ncol = 2)
@
\caption{\label{fig:barrel2}All lands from the first bullet shot from barrel 2 are compared to Bullet 2-1 (barrel 2). The largest number of CMS is eleven, observed with Bullet 1-6. }
\end{figure}

>>>>

\hh{The main idea of locally weighted regression is to use a weighting routine that  emphasizes the effect of points close by and de-emphasizes the effect of points as they are further away. The weighting function used here, is the tricubic function $w(d) = \left(1 - d^3\right)^3$, for $d \in [0,1]$ and $w(d) = 0$ otherwise.  $d$ is defined as the distance between $x_i$ and the location of the fit $x_o$ and the maximum distance of the range of the $x$-values for span $\alpha$ in $x_o$. }

%\hh{XXX standard errors: are based on independence of errors (which we don't have because of the high autocorrelation) and the assumption that the amount of bias is neglible. Which we don't know. We can produce standard errors, but (a) the nominal confidence level will be violated, and (b) the errors only allow for pointwise errors. We need a different approach. XXX}

Figure~\ref{fig:loess_fit} provides a look at the loess fit, in blue, overlaid against the processed image of bullet~1-5. The fit seems to do a reasonable job of capturing the structure of the image. \hh{The blue area around the signature are  95\% bootstrapped confidence intervals based on 1,000 bootstrap samples. }
Figure~\ref{fig:loess_resid} shows the residuals from this fit. These residuals are called the \emph{signature} of bullet~1-5.
%
\begin{figure}[hbtp]
  \centering
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{\label{fig:loess_fit} Loess fit for bullet~1-5.}
<<loess_fit, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE,  message=FALSE>>=

@@

my.loess$fitted + ylab("Surface measurements")
@
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{\label{fig:loess_resid} Residuals of loess fit for bullet~1-5.
This defines the {\it signature} of bullet~1-5. Blue areas show  95\% bootstrap confidence intervals (based on $B=1,000$ bootstrap samples).
}
%<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
%my.loess$resid + ylab("Residuals of loess Fit") 
%@
<<boot_loess, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\textwidth', warning=FALSE>>=
boot.loess <- boot_fit_loess(br111_bullet, br111.groove)
poly <- with(boot.loess, data.frame(x = c(y,rev(y)), y=c(high, rev(low))))
qplot(x=x, y=y, geom="polygon", fill=I("steelblue"), data=poly) +
  geom_line(aes(x=y, y=resid), data=my.loess$data) +
  ylab("Residuals of loess fit") + xlab("y") + theme_bw()
@
\end{subfigure}
\caption{Fit and residuals of a loess fit to bullet~1-5 (Barrel~1).}
\end{figure}
%

%' \hh{XXX Do we need the next example? We could save some space here XXX}
%' Figure~\ref{fig:loessfits} shows the signatures of all lands of bullet 2 (in grey) fired from the same barrel as bullet~1. The darker line overlaid on each of the signatures, shows signature from bullet~1-5. 
%' %We can reproduce a similar figure to the one from the circular fits by overlaying the residuals from each loess fit for bullet 2 onto an image of the loess residuals from bullet~1-5. This is shown in Figure~\ref{fig:loessfits}. 
%' Bullet 2-1 is the best match for bullet~1-5, but the alignment is not quite  correct. \hh{This is one of the issues we are addressing next.}
%' 
%' \begin{figure}[hbtp]
%'   \centering
%' <<loessfits, echo=FALSE, fig.width=10, fig.height=5, out.width='\\textwidth', warning=FALSE>>=
%' br121.groove <- get_grooves(br121_bullet)
%' br122.groove <- get_grooves(br122_bullet)
%' br123.groove <- get_grooves(br123_bullet)
%' br124.groove <- get_grooves(br124_bullet)
%' br125.groove <- get_grooves(br125_bullet)
%' br126.groove <- get_grooves(br126_bullet)
%' 
%' my.loess1 <- fit_loess(br121_bullet, br121.groove)
%' my.loess2 <- fit_loess(br122_bullet, br122.groove)
%' my.loess3 <- fit_loess(br123_bullet, br123.groove)
%' my.loess4 <- fit_loess(br124_bullet, br124.groove)
%' my.loess5 <- fit_loess(br125_bullet, br125.groove)
%' my.loess6 <- fit_loess(br126_bullet, br126.groove)
%' 
%' my.loessactual <- fit_loess(br111_bullet, br111.groove)
%' 
%' minrows <- min(length(my.loess1$data$resid),
%'                length(my.loess2$data$resid),
%'                length(my.loess3$data$resid),
%'                length(my.loess4$data$resid),
%'                length(my.loess5$data$resid),
%'                length(my.loess6$data$resid),
%'                length(my.loessactual$data$resid))
%' 
%' my.df <- data.frame(y = my.loess1$data$y[1:minrows], resid1 = my.loess1$data$resid[1:minrows],
%'                     resid2 = my.loess2$data$resid[1:minrows], resid3 = my.loess3$data$resid[1:minrows],
%'                     resid4 = my.loess4$data$resid[1:minrows], resid5 = my.loess5$data$resid[1:minrows],
%'                     resid6 = my.loess6$data$resid[1:minrows])
%' 
%' melt.df <- my.df %>%
%'     gather(key = part, value = resid, resid1:resid6)
%' melt.df$part <- gsub("resid", "", melt.df$part)
%' 
%' actual.df <- my.loessactual$data[1:minrows,]
%' melt.df$land <- melt.df$part
%' qplot(y, resid, data=melt.df, #colour=factor(x), 
%'       geom="line", size=I(.75), colour=I("grey70")) + 
%'   facet_wrap(~land, ncol=3, labeller="label_both") + 
%'   scale_colour_brewer(palette="Paired") +
%'   theme_bw() + theme(legend.position="bottom") + 
%'   geom_line(data = actual.df, aes(y, resid), colour="black", size=.75, alpha=0.5) + ggtitle("Signatures of bullet 1 in grey, bullet 1-5 in black") + 
%'   ylab("Residuals of loess fit") +
%'   theme(plot.margin = unit(c(0,0,0,0), unit="cm"))
%' @    
%' \caption{\label{fig:loessfits} Residuals of a loess fit to bullets 1 and 2 from barrel 1. Bullet~1-5 is shown in black. }
%' \end{figure}
%'

@@

\begin{figure}[hbtp]
\centering
    \begin{subfigure}[t]{\textwidth}\centering
\caption{Loess smooth of signatures  at $x = 100$ (span is 0.03).\label{fig:smooth}}{%
<<smooth, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3.5, out.width='.65\\textwidth', warning=FALSE>>=
qplot(data=lofX, y, resid, colour=I("grey30"), size=I(0.75), geom="line", group=bullet) +
  geom_line(aes(y=l30), colour="grey70", size=0.5) +
  facet_grid(bullet~.) +
#  scale_colour_manual("", values=cols) +
  theme_bw() + ylab("") + 
  theme(legend.position="none")
@
    }
\end{subfigure}
\begin{subfigure}[t]{\textwidth}\centering
\caption{Using a rolling median peaks and valleys are identified for each signature. Peaks and valleys on the signature correspond to striation marks on the bullet's surface. \label{fig:smoothcutb}}{%
<<smoothcut, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3.5, out.width='.65\\textwidth', warning=FALSE>>=
#images <- file.path(datadir, dir(datadir))
  lof <- processBullets(paths = images[c(5,7)], x = 100)
  lof <- bulletSmooth(lof)
  bAlign = bulletAlign(lof)
  lofX <- bAlign$bullet

@@

  ggplot() + theme_bw() +
    geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), ymin=-6, ymax=6, 
              data=peaks,  alpha=0.2) +
    geom_vline(aes(xintercept=extrema, colour=factor(type)), 
               data= peaks, alpha=0.7) +
    scale_colour_brewer(palette="Set2") + 
    scale_fill_brewer(palette="Set2") +
    theme(legend.position="none") + 
    facet_grid(bullet~.) +
    geom_line(aes(x=y, y=l30, group=bullet), data=lofX) +
  ylab(expression(paste("Signatures (in ",mu,"m)", sep=""))) 
@
}
\end{subfigure}    
\begin{subfigure}[t]{\textwidth}\centering
    \caption{Rectangles in the back identify a striation mark on one of the bullets.  Matching striation marks are indicated by color filled rectangles and marked by an `o'. Mismatches are filled in grey and  marked by an `x'.   \label{fig:smoothcutd}}{%
<<smoothmatch, echo=FALSE, dependson='twolands100match', fig.width=7, fig.height=2.75, out.width='.65\\textwidth', warning=FALSE>>=
peaks1$lines$bullet <- b12[1]
peaks2$lines$bullet <- b12[2]

@@

All of the other steps are done on pairs of bullet lands:
\begin{enumerate}
\item {\bf Smooth the two signatures} by a loess with a very small span (see Figure~\ref{fig:smooth}). 
\item Use cross-correlation to {\bf find the best alignment} of the two signatures: shift one of the signatures by the lag indicated by the cross-correlation function (see Figure~\ref{fig:ccf} for the cross-correlation function and Figure~\ref{fig:crosscutX} for the resulting shift).
\item Using a rolling average, {\bf identify peaks and valleys} for each of the signatures. We then define an interval around the location of the extrema on each side as one third of the distance to the location of the next extrema (see Figure~\ref{fig:smoothcutb}). 
\item {\bf Match striations across signatures:} based on the intervals around the extrema as defined above, we identify joint intervals between two signatures as those areas, in which two or more of the individual intervals overlap: a joint interval is defined as the smallest interval that encompasses all of the overlapping intervals. A joint interval is then called a match(ing stria) between the signatures, if all of the intervals are of the same type of extrema, i.e.\ they are either all peaks or all valleys. In Figure~\ref{fig:match} all matches are shown as color-filled rectangles corresponding to their type of extrema (peaks are shown in orange, and valleys in green). Non-matching intervals are left grey.
\item {\bf Extract features from the aligned signatures and the matches between them:} there is a slew of different features one could extract. Here, we describe a few of the ones that can be found in the literature and some that we found to be of practical relevance:
\begin{enumerate}[label=(\roman*)]
\item maximal number of CMS (consecutive matching striae), and, similarly, the number of consecutively non-matching striae (CNMS), 
\item number of matches and non-matches,
\item average difference between signatures $D$, defined as the Euclidean vertical distance of surface measurements between aligned signatures. Let $f(t)$ and $g(t)$ be smoothed, aligned signatures:
\[
D^2 = \frac{1}{\text{\#}t}\sum_t \left(f(t) - g(t)\right)^2,
\]
\item the sum $S$ of matched extrema: for each of the matched stria, determine the average of the absolute height of the peak or valley. $S$ is then defined as the sum of all these averages. 
\end{enumerate}
\end{enumerate}
%
The difference $D$ between signatures is here defined as the Euclidean distance (in $\mu m$). In the paper by \citet{ma:2004}, distance is defined as a measure relative to the first signature, which serves as a comparison reference and is therefore a unitless quantity.

@@

%' \begin{figure}[hbtp]
%'   \centering
%' <<barrel2, echo=FALSE, fig.width = 10, fig.height=6, out.width='\\textwidth', warning=FALSE>>=
%' 
%' list_of_matches <- lapply(25:30, function(i) {
%'   lof <- processBullets(paths = images[c(31,i)], x = 100)
%'   lof <- bulletSmooth(lof)
%' 
%'   bAlign = bulletAlign(lof)
%'   lofX <- bAlign$bullet  
%' 
%'   b12 <- unique(lof$bullet)
%'   peaks1 <- get_peaks(subset(lofX, bullet==b12[1]), smoothfactor = 25)
%'   peaks2 <- get_peaks(subset(lofX, bullet == b12[2]), smoothfactor = 25)
%'   peaks1$lines$bullet = b12[1]
%'   peaks2$lines$bullet = b12[2]
%'   lines <- striation_identifyXXX(peaks1$lines, peaks2$lines)
%' 
%'   ggplot() +
%'     theme_bw() + 
%'     geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), show.legend=FALSE, ymin=-6, ymax=6, data=lines, alpha=0.2) +
%'     geom_line(aes(x = y, y = l30, linetype = bullet),  data = lofX, alpha=0.6) +
%'     scale_linetype_discrete("") +
%'     scale_fill_brewer("", palette="Set2", na.value=alpha("grey50", alpha=0.5)) +
%'   theme(legend.position = c(1,1.2), legend.justification=c(1,1),
%'         legend.background = element_rect(fill=alpha('white', 0.4))) + 
%'     ylim(c(-6,6)) + ylab("") + xlab("") +
%'     geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(lines, !match)) +
%'     geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(lines, match)) +
%' #    theme(plot.margin=unit(c(1,0,0,0), unit="line")) +
%'     theme(plot.margin=unit(c(0,0,0,0), unit="cm"))
%' })
%' 
%' grid.arrange(list_of_matches[[1]], list_of_matches[[2]], list_of_matches[[3]], 
%'              list_of_matches[[4]], list_of_matches[[5]], list_of_matches[[6]],
%'              ncol = 2)
%' @
%' \caption{\label{fig:barrel2}All lands from the first bullet shot from barrel 2 are compared to Bullet 2-1 (barrel 2). The largest number of CMS is eleven, observed with Bullet 1-6. \hh{XXX Do we need this example? This might be a place to cut XXX}}
%' \end{figure}
